---
title       : R for beginners
subtitle    : 3rd workshop by R-Ladies Lisbon
author      : Presented by Isabel Lafaia
job         : Version 0
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---


## R for beginners

### By R-Ladies Lisbon

<div class="footer">Based on the cheat sheet:
<a href="https://www.rstudio.com/wp-content/uploads/2016/05/base-r.pdf"> Base R </a>

---

## Contents

### Topics covered:

* Simple data types
* Data structures (e.g. data frames)
* Control statements (if, while, for)
* Functions
* Reading data from files
* Libraries, getting help, working directory

---

```{r child = 'Sections/SimpleDataTypes.Rmd'}
```

---

```{r child = 'Sections/VariableAssignment.Rmd'}
```

---

```{r child = 'Sections/DataStructures.Rmd'}
```

---

```{r child = 'Sections/Vectors.Rmd'}
```

---

```{r child = 'Sections/Matrixes.Rmd'}
```

---

```{r child = 'Sections/DataFrames.Rmd'}
```

---

```{r child = 'Sections/ControlStatements.Rmd'}
```

---

```{r child = 'Sections/IfStatement.Rmd'}
```

---

```{r child = 'Sections/WhileLoop.Rmd'}
```

---

```{r child = 'Sections/ForLoop.Rmd'}
```

---

```{r child = 'Sections/Functions.Rmd'}
```

---

```{r child = 'Sections/ReadingWritingData.Rmd'}
```

---

```{r child = 'Sections/WorkDirectory_Help_Libraries.Rmd'}
```

---

## Summary

### Topics covered:

* Simple data types
* Data structures (e.g. data frames)
* Control statements (if, while, for)
* Functions
* Reading data from files
* Libraries, getting help, working directory

